|

### 2021-09-29 front-and-back-matter/_00-introduction.Rmd
Back to working version General clean-up Proper counting of words included in tables

get_words_short <- function(){

files <- list.files(path = here::here(), pattern = "\\.Rmd$")

files <- files[which(!(files %in% c("_main.Rmd","index.Rmd")))]

words_v <- c()

for (file in 1:length(files)) {
  tmp <- wordcountaddin::word_count(here::here(files[file]))
  words_v <- c(words_v, tmp)
}

words <- sum(words_v)

return(words)

}

get_words <- function(){

files <- list.files(path = here::here(), pattern = "\\.Rmd$")

files <- files[which(!(files %in% c("_main.Rmd","index.Rmd", "tmp.Rmd")))]

words_v <- c()

for (file in 1:length(files)) {
  tmp <- wordcountaddin::word_count(here::here(files[file]))
  words_v <- c(words_v, tmp)
}

# TODO Work out what an appropriate number of words for tables is
# Sum words and add number of words in tables
words <- sum(words_v) + 250

date <- as.character(format(Sys.time(),"%Y%m%d"))
time <- as.character(format(Sys.time(),"%H%M"))

tmpWords <- data.frame(words = words,
                       date = date,
                       time = time)

masterWords <- read.csv(here::here("data","words","words.csv"),
                        header = TRUE)

masterWords <- rbind(masterWords,
                     tmpWords) %>%
  dplyr::group_by(date) %>%
  slice(which.max(time)) %>%
  dplyr::ungroup()

return(masterWords)

}

@@

@@

>>>>

source(here::here("R/helper.R"))

@@

table_words <- table_words()

@@

Table words: `r table_words`
